Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-03-12 TEBenchmarkPaper/article.tex
Better "second guessing" phrasing

We normalised the conjectures generated by each tool, as well as the theorems
from the ground truth, by numbering their free variables from left to right and
using de Bruijn indices for bound variables. Since both tools can only output
equations, we also sorted their left- and right-hand-sides into lexicographical
order. Precision and recall were calculated by syntactically comparing the sets
of generated conjectures to those of their ground truth. Other than equation
symmetry, we specifically \emph{ignored} logical relationships between
syntactically distinct statements, such as one equation being implied by
another. The main reason is to avoid second-guessing the ground truth: the
theorems' authors chose to state them that way, and it is not our place to
decide whether an alternative form is ``just as good'' (for example, a more
general statement is more widely applicable, but it might also be harder to
understand).

>>>>

We normalised the conjectures generated by each tool, as well as the theorems
from the ground truth, by numbering their free variables from left to right and
using de Bruijn indices for bound variables. Since both tools can only output
equations, we also sorted their left- and right-hand-sides into lexicographical
order. Precision and recall were calculated by syntactically comparing the sets
of generated conjectures to those of their ground truth. Other than equation
symmetry, we specifically \emph{ignored} logical relationships between
syntactically distinct statements, such as one equation being implied by
another. Whilst logically sound, second-guessing the ground truth in this way
would harm the other aspects which we care about which influence interestingness
(for example, a more general statement is more widely applicable, but it might
also be harder to understand).
